### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@a584545019c68fc3513be98c58545cb51310a121 🚀

Reassuringly, these predictions are validated by the sites where the
three highly pathogenic coronavirus are believed to have recently
emerged. While available information puts the spillover of SARS-CoV-2 in
a live animal market in Wuhan, China, the ultimate origin of the virus
is almost certainly in a Lineage 2 sarbecovirus from a southeast Asian
horseshoe bat. Similarly, the SARS-CoV outbreak began in Guangdong
province in 2002, reaching humans through small carnivore bridge hosts,
but was eventually traced back to a set of likely progenitor viruses
found in cave-dwelling horseshoe bats in Yunnan province (cite Hu et
al.~2017 PLoS Pathogens); nearby, antibody evidence has indicated human
exposure to SARS-like viruses.\textsuperscript{21} MERS-CoV was
originally detected in Saudi Arabia, accompanied by a nearly identical
virus sequenced from an Egyptian tomb bat (\emph{Taphozous perforatus})
(cite Memish et al.~2013 EID), but is widespread in camels in East
Africa and the Middle East, and may have reached its bridge host decades
earlier than originally supposed (cite Muller et al 2014 EID); as a
result, the geography of the original bat-to-camel transmission is still
widely regarded as uncertain. All of these are broadly consistent with
the risk factors we identify. Notably, India and west Africa are
additional hotspots that have yet to experience the emergence of a bat
coronavirus into human populations, but may still be at
risk---particularly given known gaps in bat
surveillance,\textsuperscript{17} and a dense population in both regions
with global connectivity. In any of these regions, surveillance on viral
reservoirs can be paired with targeted monitoring of high-risk human
populations (i.e., those with regular wildlife
contact)\textsuperscript{22} for maximum impact.

>>>>

Reassuringly, these predictions are validated by the sites where the
three highly pathogenic coronavirus are believed to have recently
emerged. While available information puts the spillover of SARS-CoV-2 in
a live animal market in Wuhan, China, the ultimate origin of the virus
is almost certainly in a divergent lineage of sarbecoviruses from the
Indochinese peninsula that was poorly characterized prior to the
pandemic {[}cite Worobey 2022 Zenodo; Temmam 2022 Nature; Boni 2020
Nature Microbiology{]}. Similarly, the SARS-CoV outbreak began in
Guangdong province in 2002, reaching humans through small carnivore
bridge hosts, but was eventually traced back to a set of likely
progenitor viruses found in cave-dwelling horseshoe bats in Yunnan
province (cite Hu et al.~2017 PLoS Pathogens); nearby, antibody evidence
has indicated human exposure to SARS-like viruses.\textsuperscript{21}
MERS-CoV was originally detected in Saudi Arabia, accompanied by a
nearly identical virus sequenced from an Egyptian tomb bat
(\emph{Taphozous perforatus}) (cite Memish et al.~2013 EID), but is
widespread in camels in East Africa and the Middle East, and may have
reached its bridge host decades earlier than originally supposed (cite
Muller et al 2014 EID); as a result, the geography of the original
bat-to-camel transmission is still widely regarded as uncertain. All of
these are broadly consistent with the risk factors we identify. Notably,
India and west Africa are additional hotspots that have yet to
experience the emergence of a bat coronavirus into human populations,
but may still be at risk---particularly given known gaps in bat
surveillance,\textsuperscript{17} and a dense population in both regions
with global connectivity. In any of these regions, surveillance on viral
reservoirs can be paired with targeted monitoring of high-risk human
populations (i.e., those with regular wildlife
contact)\textsuperscript{22} for maximum impact.
